%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Cameron Wolff} \\ \vspace{1pt}
    \small 949-922-0667 $|$ \href{mailto:x@x.com}{\underline{cameron.wolff@proton.me}} $|$ 
    \href{https://www.linkedin.com/in/camwolff02/}{\underline{linkedin.com/in/camwolff02}} $|$
    \href{https://github.com/camwolff02}{\underline{github.com/camwolff02}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic State University (Cal Poly)}{San Luis Obispo, CA}
      {Master of Science in Computer Science}{06/2026}
    \resumeSubheading
{California Polytechnic State University (Cal Poly)}{San Luis Obispo, CA}
      {Bachelor of Science in Computer Science}{06/2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Associate Intern}{06/2024 -- 09/2024}
      {BMSIS Young Scientist Program at NASA Ames Research Center}{}
      \resumeItemListStart
        \resumeItem{Designed data pipeline to take Plotly graph from an R script to Django to a HTML client, enabling users to dynamically update visualizations stored on the server.}
        \resumeItem{Ported genetic data graphs from static PNG to interactable Plotly webpages, enabling Scientists to explore data.}
        \resumeItem{Developed and deployed full stack web application to Ames’s servers, enabling integration with the NASA GeneLab Visualization Portal.}
        \resumeItem{Presented live web app demo virtually to end users, NASA Ames Data Processing staff.}
      \resumeItemListEnd

  \resumeSubheading
      {Undergraduate Research Intern}{11/2022 -- 10/23}
      {SDO Exploration and Research Community for Heliophysics}{}
      \resumeItemListStart
        \resumeItem{Developed an AI search engine that enables content-based image retrieval of solar images for astronomers.}
        \resumeItem{Followed unit test driven development, used AGILE sprints and mob programming for fast paced collaborative development.}
        \resumeItem{Trained a simple siamese neural network on the SDO/AIA satellite dataset, ensuring astronomers could see accurate search results.}
    \resumeItemListEnd

    \resumeSubheading
      {Volunteer Research Assistant}{06/2023 -- 09/2023}
      {Directed Acyclic Graphs Project through the NASA Open Science Data Repository  AWG}{}
      \resumeItemListStart
        \resumeItem{Researched using AI to generate DAGs for modeling astronaut medical risks, enabling biologists to understand human health in space.}
        \resumeItem{Presented research on effectiveness of MMHC algorithm at American Gravitational and Space Research Conference.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
  
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Software Lead} $|$ Cal Poly Space Systems | \emph{C++,  Linux, Git,  ROS2, micro-ROS, esp32}}{03/2024 -- Present}
          \resumeItemListStart
           \resumeItem{Designed and presented flight software architecture for Altitude Determination and Control System to SpaceX engineers for external feedback.}
            \resumeItem{Designed and implemented distributed flight and ground software, moving rocket data to graphical visualizer.}
            \resumeItem{Lead team during summer through development of new flight computer and flight software OS, enabling re-usability for future rockets.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Personal Mobile Robot} $|$ \emph{C++, Python,  Linux, Git, ROS2, micro-ROS, Rviz, Servos}}{07/2023 -- Present}
          \resumeItemListStart
            \resumeItem{Built Raspberry Pi robot, controlled wirelessly by a Linux base station with camera feed for remote operation.}
            \resumeItem{Calculated and implemented differential drive kinematics for velocity control and odometry, enabling 3D visualization of movement.}
            \resumeItem{Iterated after real world testing, moving to ackermann kinematics (car controls) for greater stability at speed.}
          \resumeItemListEnd

       \resumeProjectHeading
            {\textbf{Rover Software Developer} $|$ SC Robotics | \emph{Python, C++,  Linux, Git,  ROS2, OpenCV, PID}}{09/2022 -- 02/2024}
          \resumeItemListStart
            \resumeItem{Developed camera calibration, distance estimation, and rover controller for autonomous driving to ArUco markers.}
            \resumeItem{Designed robust and scalable backend for arm and end-effector,  creating link between physical and simulated twin.}
            \resumeItem{Obtained operational insight, piloting the rover through the URC 2023 finals as the only community college team.}
             \resumeItem{Mentored new students through workshops on ROS2 and Python, ensuring the success of future teams.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, Java, R, JavaScript, ARM Assembly, HTML/CSS, XML, JSON, URDF } \\
     \textbf{Frameworks}{: Django, unittest, ROS2, micro-ROS, JavaFX, JUnit, JQuery } \\
     \textbf{Developer Tools}{: Git, Linux server, VIM, VS Code, PyCharm, IntelliJ, Jupyter, Docker, Python venv, conda, Gazebo} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Plotly, OpenCV, Streamlit, Scikit-learn, Pytorch Lightning}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
